---
title: "Multiple Linear Regression"
author: "Youngshin Kim"
date: "December 8, 2016"
output: pdf_document
---

#Abstract

The mission for this project is to reproduce results from Section 3.2 (pages 71 to 82), from the book "An Introduction to Statistical Learning" (by James et al).  

#Introduction

The main analysis of this project is multiple linear regression. Multiple linear regression is different
from simple linear regression in that it involves more than one predictor, as the name suggests.  
We will use the Advertising data that contains TV, Radio, Newspaper budget data and these will be the 
predictors.  

#Data

The Advertising data consists of values on Sales (in thousands of unit) of 
some product in 200 different markets and values on advertising budget 
(in thousands of dollars) for three different kind of 
marketing strategies: TV, Radio, Newspaper. For the purpose of this project, 
we are just interested in the advertising budget for TV. 

```{r, echo=FALSE, warning=FALSE, results = 'asis', comment = NA}
load('../data/regression.RData')
options(xtable.comment = FALSE)
library(xtable)

xtable(tv_reg_summary$coefficients, caption = "Simple regression of sales on TV")
xtable(radio_reg_summary$coefficients, caption = "Simple regression of sales on radio")
xtable(newspaper_reg_summary$coefficients, caption = "Simple regression of sales on newspaper")
```

#Methodology

We use multiple regression model to model the relationship between Sales and the three predictors.
The response variable here is Sales and the predictor variables are TV, Radio, and Newspaper budgets.  
The regression equation is Sales = Intercept + Coefficient * TV + Coefficient * Radio + Coefficient * Newspaper.
With this equation in mind, we use the lm function in R to find the relevant
information for our regression.  The syntax for this code is
lm(Sales ~ TV + Radio + Newspaper, data = advertising) where object 'advertising' is the 
main data from Advertising.csv.  The basic idea behind this function is 
that we want to find the intercept and the regression coefficients that
minize the residual sum of squares.

#Results

```{r, echo=FALSE, results = 'asis', comment = NA}
xtable(adv_reg_summary$coefficients, caption = 'Regression table')
```

```{r, echo=FALSE, results = 'asis', comment = NA}
load('../data/correlation-matrix.RData')
xtable(correlation, caption = "Correlation Matrix")
```

```{r, echo=FALSE, results = 'asis', comment = NA}
source('../code/functions/regression-functions.R')
xtable(data.frame("Value" = c(rse(adv_reg), rsquared(adv_reg), fstat(adv_reg)), 
                  row.names = c("RSE", "R^2", "F-statistic")), caption = "Various Statistic")
```

##Is at least one of the predictors useful in predicting the response?
We can be pretty confident that at least one of the predictors is useful in predicting the response,
because in Table 4, p-value for TV and Radio are zero, which mean they are statistically significant. 

Also, F-statistics is above 1 and in fact it is extremely high.  This also shows that
there is a relationship between predictors and response.

##Do all predictors help to explain the response, or is only a subset of the predictors useful?
In Table 4, p-value for Newspaper is extremely high so Newspaper budget is probably not an important
indicator of Sales growth.  In fact, the coefficient for Newspaper is negative, so an increase in 
Newspaper budget probably lowers Sales growth.

##How well does the model fit the data?
The model seems to fit the data pretty well, because RSE is low and R^2 is high.
It also helps to notice that TV and Radio are correlated.  The model that includes
both variables has a lower RSE than the model that only contains TV.

##How accurate is the prediction?
If we were to do a prediction using this model, the result should be pretty satisfactory 
because the regression summary tells us that our coefficients for intercept, TV, and Radio
are statistically signifcant.  The predition would be better if we use the model without
including Newspaper.


#Conclusions

All the predictors have effects on our response variable Sales.  This was
made clear with simple linear regression.  Working together, however, Newspaper
proved to be harmful for Sales.  TV and Radio, on the other hand, proved to have 
a synergy effect in Sales growth.